% !TEX program = xelatex

\documentclass{resume}
\linespread{1.30}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Moyang He}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address

\contactInfo{iammoyang@ccs.neu.edu}{206~-~390~-~0024}{ Seattle, WA, 98109}

% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

%\section{Objective}
%%Software Development Engineer, Summer/Fall Intern
%Software Development Engineer Intern

\section{Education}
\datedsubsection{M.S., Computer Science, Northeastern University(GPA 4.0), Seattle}{Sep 2015 -- Jun 2017}

\datedsubsection{B.S., Mathematics and Applied Mathematics(GPA 3.6), Xiamen University, China}{2011 -- 2015}

\vspace{0.1in}

\section{TECHNICAL SKILLS}

\textbf{Languages \& Tools:}~~~Java,~~Python,~~C/C++/STL,~~SQL,~~Scheme,~~\LaTeX


%\vspace{0.05in}

%\textbf{Data Science:}~~~Scipy/Numpy,~~Scikit-learn,~~Matlab,~~R,~~Mathematica

%\vspace{0.05in}

\textbf{Knowledge:}~~~OOP/OOD,~~Design Patten,~~Algorithm~\&~Data Structure,~~Functional Programming

~~~~~~~~~~~~~~~~~~~~~~~Concurrency programming,~~Computer System,~~Machine Learning,~~Web Development.

%\vspace{0.05in}

%\textbf{IDE:}~~~Eclipse,~~PyCharm,~~IDLE,~~WebStorm

\section{Projects}


\datedsubsection{\textbf{Online Course Registration Web Application}}{Spring 2016}
Skill \& Tools:~~~Bootstrap,~~jQuery,~~Angular.js,~~Node.js,~~MongoDB

\begin{itemize}
%  \item System design and development with Angular.js, Node.js, and MongoDB.
  \item Developed a onp-page application with Angular.js  in MVC architecture and used Bootstrap frameworks for responsive layout. Facebook  API is  also used for sharing with social media.
  \item Create asynchronous server with Node.js for back end and deployed MongoDB database in OpenShift cloud platform.
\end{itemize}

\datedsubsection{\textbf{Space Invaders Desktop Game In Java}}{2015 - 2016}
Skill \& Tools:~~~Design patten in Java,~~JUnit Test Framework,~~Swing GUI,~~pip,~~Git

\begin{itemize}
  \item Designed and created a game in Java and developed with JUnit in Eclipse.
  \item Developed GUI with Swing  framework and Java 2D graphics library.
  \item Refactored code with new functional programming features provided by Java 8, improved parallel performance by 40\%.  
\end{itemize}

\datedsubsection{\textbf{Python-based Study and Implementation  of Quantitative Trading}}{2014 - 2015}
Skill \& Tools:~~~Functional programming, Concurrency programming Scipy/Numpy,~~Scikit-learn

\begin{itemize}
  \item Built a multi-threaded Python crawler with urllib2 and scrapy library to craw stock news website, then parse HTML with BeautifulSoup and retrieve information.
  \item Implemented random forest algorithm to analyze stock market news using Python and R machine learning package,  proposed a trading strategy for statistical arbitrage, and created a Django-based websites to posted real time trading simulation.
\end{itemize}



\datedsubsection{\textbf{Mathematical Contest Honor}}{2013, 2014}
\begin{itemize}
  \item Led a team to participate two Mathematical Contests in Modeling.
  \item Designed and implemented a graph theory based algorithm to recover information from teared paper. First  Price, 1.5\% in 25558 teams
    \item Conducted and implemented a traffic flow simulation and statical analysis program to investigated how different traffic rule affect traffic efficiency. Meritorious Winner,  7\% of 6755 global teams
\end{itemize}


%\datedline{Meritorious Winner,~~~Mathematical Contest in Modeling}{2014}
%
%\datedline{First Prize,~~~China Contemporary Undergraduate Mathematical Contest in Modeling}{2013}


\end{document}
