% !TEX program = xelatex

\documentclass{resume}
\linespread{1.35}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Moyang He}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address

\contactInfo{iammoyang@ccs.neu.edu}{206-390-0024}{301 Minor Ave N. UNIT 803, Seattle, WA, 98109}

% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

\section{Education}
\datedsubsection{M.S., Computer Science (GPA 4.0), Northeastern University, Seattle}{2015 -- 2017}

\datedsubsection{B.S., Mathematics and Applied Mathematics, Xiamen University, China}{2011 -- 2015}

\vspace{0.1in}

\section{TECHNICAL SKILLS}

\textbf{Languages:}~~~Python,~~Java,~~C/C++/STL,~~SQL,~~Scheme,~~\LaTeX

%\vspace{0.05in}

\textbf{Web Development:}~~~HTML/CSS,~~Bootstrap,~~Angular.js~~jQuery,~~Node.js,~~Django,~~MongoDB

%\vspace{0.05in}

\textbf{Software Development:}~~~JUnit,~~Swing,~~pip,~~GCC/G++,~~Git

%\vspace{0.05in}

\textbf{Data Science:}~~~Scipy/Numpy,~~Scikit-learn,~~Matlab,~~R,~~Mathematica

%\vspace{0.05in}

\textbf{Knowledge:}~~~OOP/OOD,~~Algorithms,~~Web Development,~~Machine Learning

%\vspace{0.05in}

\textbf{IDE:}~~~Eclipse,~~PyCharm,~~IDLE,~~WebStorm

\section{Projects}


\datedsubsection{\textbf{Online Course Registration Web Application}}{Sep 2015 -- Jan 2016}


\begin{itemize}
  \item System design and development with JavaScript, Node.js, MongoDB and deployed in OpenShift.
  \item Developed front end with Angular.js and Bootstrap. Facebook/Google Map APIs are also used.
  \item Designed data schema with MongoDB.
\end{itemize}

\datedsubsection{\textbf{Space Invaders Desktop Game }}{Sep 2015 -- Jan 2016}


\begin{itemize}
  \item Designed and created a game in Java and developed with JUnit in Eclipse.
  \item Developed GUI with Swing GUI framework and Java 2D graphics library.
  \item Refactored code with new features provided by Java 8, improve parallel performance by 40\%.  
\end{itemize}

\datedsubsection{\textbf{Python-based Stock Information Web Crawler}}{Nov 2013 -- Aug 2014}

\begin{itemize}
  \item Built a Python crawler with urllib2 library and parse HTML using BeautifulSoup and Regular expression.
  \item Implemented various methods to analyze stock market information using Python machine learning package.
  \item Proposed a trading strategy and created a Django-based websites to posted real time trading simulation.
\end{itemize}





\section{Honors and Awards}
\datedline{Meritorious Winner,~~~Mathematical Contest in Modeling}{2014}

\datedline{First Prize,~~~China Contemporary Undergraduate Mathematical Contest in Modeling}{2013}


\end{document}
