%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Industrial Experience}


%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Business Intelligence Engineer II} % Job title
{Amazon Inc.} % Organization
{Seattle, WA} % Location
{Sept. 2021 - Now} % Date(s)
{
\begin{cvitems}
	\item{Iterate Amazon Seller Central e2e user experience by working with SDEs and PMs to define, implement, monitor and display metrics to Amazon \nth{3} Party Sellers}
	\item{Build data pipelines from online prod to offline data lake, drive communication with internal partners to schematize and automatically generate reports and dashboards for decision-making.}
	\item{Lead new feature development in Seller Central by using hierarchical clustering, summarized findings and effectively communicated in a compelling way to senior leaders and drove business actions.} 
	\item{Navigate engineering teams through presentation of data-based recommendations, communicating state of business, experiment results and implement best practices.}	
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Data Scientist} % Job title
{Foursquare Labs Inc.} % Organization
{Seattle, WA} % Location
{Nov. 2020 - Aug. 2021} % Date(s)
{
\begin{cvitems}
	\item{Conducted Product Iteration and validated the effectiveness on our attribution portal new features by collaborating with PMs.}
	\item{Performed Campaign Monitoring using Waze as 3p measurement solution partnership, interpreted campaign result metrics such lift, total visits, incremental visits, cost per visits and cost per incremental visit using z-test and machine learning models to derive insight for future customer targeting.}
	\item{Actively built processes and tools to make data more accessible and interpretable, communicated with internal partners to define appropriate data reports and dashboards that became integral to the decision-making process.}		
\end{cvitems}
}

%------------------------------------------------  

\cventry
{Senior Data Consultant} % Job title
{American Express (EXL Service)} % Organization
{New York City, NY} % Location
{Sept. 2017 - Nov. 2020}
{
\begin{cvitems}
	\item{Unsupervised Learning: Used K-means method to segment customers with different AMEX marketing shares and implement different marketing strategies with the existing online first touch and linear attribution models.}
	\item{Supervised Learning: Predicted 2019Q4 short-term debt for small business owner by developing an XGboost model with 38\% GINI based on financial history, assisted with the sales team on engaging 1.5\% more customers compared to the holiday season in 2018}
	\item{A/B Testing: Worked with creative and e-commerce teams using A/B split testing on mail content, landing page, promotion as well as cross-channel marketing combining direct mails, emails and display ads}
	\item{Marketing Analysis: Initiated campaign plans and forecast as well as new strategies to achieve 200\% ROI goal, oversaw \$16M annual budget, utilized 99\% of the budget and saved 84\% of the cost per funded loan.}
	\item{Data Visualization: Created campaign performance dashboards, conducted loan and application performance analysis using Snowflake and Tableau, presented results to senior management.}		
\end{cvitems}
}


%------------------------------------------------    

\cventry
{Risk Analyst, Predictive Modeling \& Credit Risks Management} % Job title
{AXCESS Financial} % Organization
{Cincinnati, OH} % Location
{Dec. 2015 - Sept. 2017} % Date(s)
{
\begin{cvitems}
	\item{Fraud Detection Dashboard: Evaluated and proposed the recommendations for the 32\% streamline effectiveness of fraud detections tools across multiple ID verifications, online fraud platform, and customer behavior analysis}
	\item{Data Tidying \& Wrangling: Used Regex to clean Json data with Hive functions, worked with Data engineer to create cleaning logic for special Japanese character}
	\item{Regression: Collaborated with 3rd party data vendor (Experian and Clarity) to prepare customer trade-line data and built new installment loan credit scorecard model to predict the probability of default for customers with customers' trade-line information}
	\item{Model Validation: Built robust validation exercise to verify the accuracy and stability of the models, on in-sample and out-of-time data, and to avoid inaccurate prediction and low model stability}
	\item{Enhanced risk decisions by incorporating new information, new techniques, and changing factors, built strong relationships and provided proactive and thoughtful communications to stakeholders and partner teams, managed multiple priorities/projects for effective end-to-end processes}
\end{cvitems}
}

%------------------------------------------------  


\end{cventries}